The problem and promise of scale in multilayer networks

### 2020-01-31 paper/manuscript.Rmd
more portable y_{}

where x is the number of fixes where individuals A and B were within a given
distance of each other, y<sub>A</sub> is the number of fixes from individual A
when individual B did not have a simultaneous fix, y<sub>B</sub> is the number
of fixes from individual B when individual A did not have a simultaneous fix,
and y<sub>AB</sub> is the number of simultaneous fixes from individuals A and B
that were separated by more than the given distance (Farine & Whitehead 2015).
Social groups were designated if two or more individuals occurred within a given
distance of one another at any given time point.

>>>>

where x is the number of fixes where individuals A and B were within a given
distance of each other, $y_{A}$ is the number of fixes from individual A
when individual B did not have a simultaneous fix, $y_{B}$ is the number
of fixes from individual B when individual A did not have a simultaneous fix,
and $y_{AB}$ is the number of simultaneous fixes from individuals A and B
that were separated by more than the given distance (Farine & Whitehead 2015).
Social groups were designated if two or more individuals occurred within a given
distance of one another at any given time point.
